### 2025-04-10 chapters/3-jets.tex
Final changes to main files for first draft

In this chapter, we get a better handle on things by giving up on thinking about individual particles.
%
We instead make progress by thinking about many particles at once!
%
These groups of particles are called \emph{jets}, and we will address them theoretically with a common strategy in quantum mechanics:
%
summing up all of the different possibilities.
%
We consider all the ways a particle could split, how each of its children could split, and so on, and add together the probabilities of each to obtain a consistent estimate of the behavior of jets.
%
This chapter initiates the study of jets and jet substructure, which we define shortly, and introduces some of the key conceptual and computational tools used in the work presented in this thesis.
%
If the exposition of this chapter is confusing or insufficient, I can highly recommend the pedagogical treatment of \Reff{Marzani:2019hun}.

@@

We will be using the building blocks of \Chap{particles};
%
particles remain the main actors of this section, and the substructure diagrams of \Sec{} will still be useful tools.
%
Most importantly, however, we will construct a model of jets using splitting functions, soft theorems and the angular-ordered principle of collinear color coherence.
%
% -- where we have already seen the use of \glslink{regularization}{\underline{regularization}} -- the removal of infinities to produce a physically sensible result.
%
We will use \glslink{resummation}{\underline{resummation}} -- the use of series techniques and calculus to obtain analytic results for the infinite series that appear when we consider an infinite number of splittings, and thus uncover the secrets of jet substructure.
%
We will also see \underline{renormalization} -- roughly, ``zooming in'' -- emerge as a useful lens for understanding the inner viscera of a jet as particles seem to split more and more as we zoom further and further in on jets.
%
Renormalization will give us additional tools to obtain finite results, and even allow us to recover the celebrated \gls{dglapeqn}.

@@

\remark{}{
    The mathematical theory of resummation goes far beyond the paltry introduction of this chapter.
    %
    Borel resummation is particularly important for understanding the full formal structure of quantum field theory (appearing, for example, in the theory of renormalons and the non-perturbative structure).
    %
    Abel resummation, named after the mathematician whose quote appears at the beginning of this section, is another common resummation method for divergent series in mathematics.
    %
    For a more mathematical and complete presentation, I can recommend the classic mathematical textbook by Hardy \cite{Hardy_1991} and the classic physics articles of \Reffs{Dunne:2012ae}{Dorigoni:2014hea};
    %
    a full list of the many wonderful resources for resummation beyond these, is far beyond our scope.
}

@@

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.7\textwidth]{example-image-a}
    \caption[
        Regions of the \(1/z\)-\(s\) plane associated with our approximations.
        %
        Adapted from \Reff{Collins:1984xc}
        %
        \sam{complete}
    ]
    {
        Regions of the \(1/x\)-\(s\) plane associated with the approximations use in this thesis.
        %
        Adapted from \underline{QCD and Collider Physics} \cite{Collins:1984xc}.
        %
        \sam{complete -- see page 132, fig 4.18}
    }
    \label{fig:dlla-plane}
\end{figure}

@@

In this section, we discuss why and how we may sew together splitting functions in order to characterize the partonic cascade.
%
Recall from \Sec{splitting-functions} that splitting functions were defined in terms of amplitudes for the production of \textit{on-shell} final states, \(\mathcal{M}_{\ell^* \to i j}\).
%
In \Eq{}, we then wrote the full differential cross section for a process producing \(N\) particles, two of which were a collinear pair \((i_1, j_1)\), in a factorized form:
%
\begin{align}
    \dd \sigma_N
    =
    \dd \sigma_{N-1}
    \,
    \dsigmatilde_{i_1\,i_2}
    \,,
\end{align}
where \(\sigma_{N-1}\) is the ``differential cross section'' when the pair \((i_1,j_1)\) have been replaced by the off-shell \(\ell^*\), and is associated with the production of \(N-1\) particles, and \(\dsigmatilde_{i_1\, i_2}\) is the splitting distribution (as in \Prop{splitting-probability-main} of \Sec{splitting-functions}) associated with the splitting.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\textwidth]{example-image-a}
    \caption{\sam{The ripple picture of angular ordering}}
    \label{fig:}
\end{figure}

@@

MLL calculations of additive jet substructure observables capture nearly all of the effects of a \glslink{accuracy}{next-to-leading logarithmic (NLL)} calculation \cite{Marzani:2019hun}.
%
Missing, however, are \vocab{non-global logarithms} -- contributions to jet substructure from partonic radiation in which a branch of the partonic tree of emissions occurs at a wider angle than would be captured by the jet, but one of whose children re-enters the jet cone.\cite{Dasgupta:2001sh,Appleby:2002ke,Weigert:2003mm,Rubin:2010fc,Banfi:2010pa,Hornig:2011iu,Kelley:2011aa,Hatta:2013iba,Schwartz:2014wha,Khelifa-Kerfa:2015mma,Larkoski:2016zzc,Marzani:2019hun,Banfi:2021owj,Banfi:2021xzn,}

@@

\remark{}{
    To include running coupling effects and work towards an MLL description of additive jet observables, we notice that the splittings of perturbative QCD should be governed by an \textit{effective coupling} \(\alpha_s(\kappa)\), where \(\kappa = \kappa(z,\theta)\) is a scale associated with the splitting.
    %
    The result would involve integrals containing terms of the form \(\int \dd z \, \dd \theta \, \alpha_s(\kappa) \, p(z) / \theta\).
    %
    The precise value we should choose for \(\kappa\) in order to account for higher-order effects is not obvious, but \Reff{} showed that \(\kappa\) should be given by the transverse momentum of the splitting in order to minimize the effects of large logarithms in perturbative calculations:
    \begin{align}
        \kappa \approx Q z(1-z)\sin\theta \approx Q z \theta
        \,.
    \end{align}
    %
    In particular, QCD correlations and cross sections that use \(\alpha_s\) evaluated at a scale \(\kappa\) generically include logarithms of the form \(\log(p_{\perp} / \kappa)\).
    %
    To make these logarithms small, one may choose \(\kappa \sim p_\perp\), which then requires that we evaluate the strong coupling at the scale \(p_\perp\) as well.
    %
    This prescription provides a straightforward procedure for understanding higher-order effects with \glspl{substructure-diagram}, and can be extended to higher perturbative accuracy with the Catani-Marchesini-Webber (CMW) prescription \cite{Catani:1990rr}, which achieves two-loop accuracy for the running of \(\alpha_s\), and to qualitatively include non-perturbative effects by \textit{freezing} the coupling, as discussed in \App{soft-distortions}.
    %
    As a reminder, the one-loop running of \(\alpha_s\) is captured by
    \begin{align}
        \alpha^{\rm 1-loop}_s(\kappa)
        =
        \frac{\alpha_s(Q)}{1 + 2\alpha_s(Q) \beta_0 \log(\frac{\kappa}{Q})}
        ,
    \end{align}
    where \(\beta_0 = (\frac{11}{3}C_A - \frac{4}{3} T_f n_f)/4\pi\) is a coefficient appearing in the QCD beta function: \(\beta(\alpha_s) = -2\beta_0 \alpha_s^2 + \mathcal{O}(\alpha_s^3)\).
    %
    \sam{Fix beta coefficient!}  % TODO
}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\textwidth]{example-image-a}
    \caption{\sam{simplifications of additive observables in partonic-cascade computations}}
    \label{fig:cascade-simplifications}
\end{figure}

@@

The \gls{parton-to-parton} is most easily characterized in terms of its \vocab{Mellin moments}, which directly capture the scaling behavior of a function (i.e. the behavior of a function as one zooms in).%
\footnote{
    Concretely, homogenous monomials, such as \(x^\ell\), have extremely simple scaling behavior:
    %
    as one scales \(x\) by a factor of \(a\), one obtains a deceptively simple relation \((a x)^\ell = a^\ell x^\ell\);
    %
    if \(a < 1\), we have ``zoomed in'' to the behavior of the function near \(x = 0\).
    %
    We say that these simple monomials are \textit{eigenfunctions of the scaling} (or dilatation) \textit{operator}.
    %
    The scaling behavior of a more complicated function \(f(x)\) -- e.g. a concrete relationship between \(f(ax)\) and \(f(x)\) -- can then be captured explicitly if it is known how \(f(x)\) can be composed in terms of the simple building blocks \(x^\ell\).
    %
    Luckily, \textit{the Mellin moments of a function \(f(x)\) precisely captures how \(f(x)\) is composed of the simple building blocks \(x^\ell\), and therefore provides a complete and simple characterization of its scaling behavior.}
}
%
Mellin moments are wonderful tools for capturing fractal structures in a wide variety of applications, and for the mathematically prodigious, it may be no surprise that they appear here.

@@

\begin{proposition}{Parton-to-Parton Fragentation at LL}{}
\begin{align}
    \label{eq:mellin_transform_defn}
    \hat{F}_{j \leftarrow i}(m;\,\rsub \leftarrow \Rjet)
    &:=
    \int_0^1 \dd x_j \, x_j^{m-1}
    \,
    F_{j \leftarrow i}(x_j;\,\rsub \leftarrow \Rjet)
    \\
    \label{eq:ll_fragmentation_function}
    &=
    \le(\frac{\alpha_s\le(Q\,\rsub\ri)}{\alpha_s\le(Q\,\Rjet\ri)}\ri)
    ^
    {\frac{\hat{p}(m)}{2\pi\beta_0}}
    _{j\leftarrow i}
    .
\end{align}
where \(Q\) is the energy carried by the initiating parton \(i\) and the subscript \(j \leftarrow i\) indicates the indices of a matrix exponential in the final line.
\end{proposition}

@@

\begin{proof}
Recalling that the jet is formed by partonic splittings which become (at LL) successively narrower, we write:
\begin{align}
    F_{f \leftarrow i}(x_f; \rsub \leftarrow \Rjet)
    &=
    \delta(1-x_f) \, \delta_{fi}
    \,\,\,
    +
    \,\,\,
    \sum_{n = 1}^\infty
    \le( 4 a_s \ri)^n
    \int^{\Rjet}_{\rsub} \frac{\dd\theta_1}{\theta_1}
    \,\,
    \int^{\theta_1}_{\rsub} \frac{\dd\theta_2}{\theta_2}
    \,\,\,
    \cdots
    \,\,
    \int^{\theta_{n-1}}_{\rsub}
    \,\,
    \frac{\dd\theta_n}{\theta_n}
    \notag
    \\
    &\qquad\qquad\qquad\qquad\qquad
    \label{eq:shower_fragmentation}
    \times
    \int_0^1 \dd x_1
    \,
    \le(\sum_{k_1}\,P_{j_1 k_1 \leftarrow i}(x_1)\ri)
    \\
    \notag
    &\qquad\qquad\qquad\qquad\qquad\qquad
    \times
    \,\,
    \cdots
    \,\,
    \int_0^1 \dd x_n
    \le(\sum_{k_n}\,P_{f\,k_n \leftarrow j_{n-1}}(x_n)\ri)
    \\
    \notag
    &\qquad\qquad\qquad\qquad\qquad
    \times
    \delta\le(x_f - \prod_{j=1}^n x_j\ri)
     ,
\end{align}
visualized diagrammatically in \Fig{shower:cartoon:fragmentation}.
%
The first term on the right-hand-side of \Eq{shower_fragmentation} represents the possibility of no splitting, where parton \(f\) is \emph{equal} to parton \(i\).
%
The terms within the sum on \(n\) each represent the possibility of \(n\) splittings in the parton shower along the path traced from parton \(i\) to parton \(f\).
%
For each term in the sum over \(n\), each of the \(n\) splittings has a probability density in its angle and energy fraction determined by \Eq{splitting_probability}, and the angular ordering \(\theta_1 > \theta_2 > \cdots > \theta_n\) is enforced by the bounds of integration on each of the angular integrals.
%
The delta function, \(\delta\le(x_f - \prod_{j = 1}^n x_j\ri)\) indicates that the final energy fraction of parton \(f\) is equal to the product of the energy fractions along the path from \(i\) to \(f\).

@@

To evaluate \Eq{shower_fragmentation}, we perform the angular integrals over the \(\{\theta_k\}_{k = 1}^n\) and use the definition of the inclusive splitting functions in \Eq{inclusive_splitting_defn}.
%
We then take Mellin moments of \(F_{f\leftarrow i}(x_f)\) in order to integrate over the delta function \(\delta \le(x_f - \prod_{k=1}^n x_k\ri)\) and enforce the relation \(x_f^{m-1} = \prod_{k=1}^n x_k^{m-1}\).
%
After the dust settles, we obtain the following expression for the Mellin moments of the parton-to-parton fragmentation function:
\begin{subequations}
\label{eq:ll_fragmentation_repeat}
\begin{align}
    \hat{F}_{f \leftarrow i}(m;\,\rsub \leftarrow \Rjet)
    &=
    \sum_{n=0}^\infty
    \le(-4\as\ri)^n
    \frac{\log^n\le(\rsub/R\ri)}{n!}
    \le(
        \int_0^1 \dd z\,
        z^{m-1} p(z)
    \ri)^n_{f\leftarrow i}
    \\
    &\approx
    \exp\le[
        \frac{\hat{p}(m)}{2\pi\beta_0}
        \log\le(
        \frac{
            \alpha_s\le(Q\,\rsub\ri)
        }{
            \alpha_s\le(Q\,\Rjet\ri)
        }\ri)
    \ri]_{f \leftarrow i}
    ,
\end{align}
\end{subequations}
where we have used the one-loop expression for \(\alpha_s(\mu)\) in \Eq{alphas_1loop} to make the replacement \(
    \log\le(\rsub/R\ri)
    =
    \log\big(
        \alpha_s\le(Q\,\rsub\ri)
        \,/\,
        \alpha_s\le(Q\,\Rjet\ri)
    \big)
    \,/\,
    8\pi\beta_0\as
    \,
    +
    \,
    \mathcal{O}(\alpha_s^2)
\), recovering the result claimed in \Eq{ll_fragmentation_function}, up to higher order corrections in \(\alpha_s\) that we neglect at this accuracy.
\end{proof}

\begin{exercise}
    % https://www.hep.phy.cam.ac.uk/theory/webber/QCDlect3.pdf#page=19
    Argue that the physics of very soft splittings -- the \(z \to 0\) limit -- is captured by the limit \(m \to 1\).
    %
    Based on physical expectations, do you expect the \(m=1\) moments of any \gls{qcd} splitting functions to diverge?
    %
    Check your intuition against the results of \Tab{inclusive-splitting}.
\end{exercise}

Applying the principles of renormalization to \Eqs{ll_fragmentation_function}{ll_fragmentation_repeat}, we can ask how the process of partonic fragmentation changes as we change the angular resolution of our ``measurements'' (i.e. the jet radius \Rjet{} and the subjet radius \rsub{}).
%
In particular, we have
\begin{subequations}
\begin{align}
    \label{eq:fragmentation_dglap_upper}
    \frac{\dd}{\dd\log\le(Q\,\Rjet\ri)} \hat{F}(m;\,\rsub\leftarrow \Rjet)
    &=
    \frac{\alpha_s(Q\,\Rjet)}{\pi}
    \,\,
    \hat{p}(m)
    \,
    \hat{F}(m;\,\rsub\leftarrow \Rjet)
    \\
    \label{eq:fragmentation_dglap_lower}
    \frac{\dd}{\dd\log\le(Q\,\rsub\ri)} \hat{F}(m;\,\rsub\leftarrow \Rjet)
    &=
    -\frac{\alpha_s(Q\,\rsub)}{\pi}
    \,\,
    \hat{p}(m)
    \,
    \hat{F}(m;\,\rsub\leftarrow \Rjet)
    ,
\end{align}
\end{subequations}
where we used \Eq{beta_fn_defn}, and have suppressed the indices of \(\hat{p}\) and \(\hat{F}\) for brevity.
%
Amazingly, we have recovered the celebrated \glslink{dglapeqn}{Dokshitzer-Gribov-Lipatov-Altarelli-Parisi (DGLAP) equations} \cite{Gribov:1972ri,Dokshitzer:1977sg,Altarelli:1977zs} for our parton-to-parton fragmentation functions:
\begin{align}
    \frac{\dd}{\dd\log\le(Q \Rjet\ri)}
    F_{f\leftarrow i}(z; \rsub \leftarrow \Rjet)
    =
    \frac{\alpha_s(Q\Rjet)}{\pi}
    \int_0^1
    \dd \frac{\dd y}{y}
    p_{j k}(y)
    F_{j\leftarrow i}\le(\frac{z}{y}; \rsub \leftarrow \Rjet\ri)
    \\
    \frac{\dd}{\dd\log\le(Q \rsub\ri)}
    F(z, \rsub \leftarrow \Rjet)
    =
    -
    \frac{\alpha_s(Q\rsub)}{\pi}
    \int_0^1
    \dd \frac{\dd y}{y}
    p_{j k}(y)
    F_{j\leftarrow i}\le(\frac{z}{y}; \rsub \leftarrow \Rjet\ri)
    \,,
\end{align}
where we have left a sum on \(k\) implicit.
%
More generally, \glspl{dglapeqn} state that the distribution of energy fractions \(z\) of partons inside a high energy composite object \(A\) obey similar integro-differential equations in which \(Q\Rjet\) is replaced by a high energy scale \(E_A\) associated with the energy of the composite object.

@@

\begin{figure}[]
    \centering
    \subfloat[]{
        % Subfigure graphic
        \includegraphics[width=.48\textwidth]{example-image-a}
        \label{fig:reclustering}
    }
    \subfloat[]{
        % Subfigure graphic
        \includegraphics[width=.48\textwidth]{example-image-a}
        \label{fig:declustering}
    }
    \caption{
        \sam{Cartoon depicting reclustering and declustering}
    }
    \label{fig:reclustering}
\end{figure}

@@

    Any algorithm which leverages \gls{declustering} is called a \vocab{de-clustering algorithm}.
\end{definitionbox}

@@

\begin{figure}[]
    \centering
    \includegraphics[width=0.8\textwidth]{example-image-a}
    \caption{\sam{Re-weighting}}
    \label{fig:reweighting}
\end{figure}

>>>>

In this chapter, we get a better handle on things by giving up on thinking about individual particles.
%
Instead, we make progress by thinking about many particles at once.
%
The groups of particles we consider are called \emph{jets}, and we will address them theoretically with a common strategy in quantum mechanics:
%
summing up all of the different possibilities.
%
We consider all the ways a particle could split, how each of its children could split, and so on, and add together the probabilities of each to obtain a consistent estimate of the behavior of jets.
%
This chapter initiates the study of jets and jet substructure, which we define shortly, and introduces some of the key conceptual and computational tools used in the work presented in this thesis.
%
If the exposition of this chapter is confusing or insufficient, I can also highly recommend the pedagogical treatment of \Reff{Marzani:2019hun}.

@@

We will be using the building blocks of \Chap{particles};
%
particles remain the main actors of this section, and the substructure diagrams of \Sec{fixed-order-substructure} will still be useful tools.
%
Most importantly, however, we will construct a model of jets using splitting functions, soft theorems and the angular-ordered principle of collinear color coherence.
%
We will use \glslink{resummation}{\underline{resummation}} -- the use of series techniques and calculus to obtain analytic results for the infinite series that appear when we consider an infinite number of splittings, and thus uncover the secrets of jet substructure.
%
We will also see \underline{renormalization} -- roughly, ``zooming in'' -- emerge as a useful lens for understanding the inner viscera of a jet as particles seem to split more and more as we zoom further and further in on jets.
%
Renormalization will give us additional tools to obtain finite results, and even allow us to recover the celebrated \gls{dglapeqn}.

@@

\remark{}{
    The mathematical theory of resummation goes far beyond the paltry introduction of this chapter.
    %
    Borel resummation is particularly important for understanding the full formal structure of quantum field theory (appearing, for example, in the theory of renormalons and the non-perturbative structure).
    %
    Abel resummation, named after the mathematician whose quote appears at the beginning of this section, is another common resummation method for divergent series in mathematics.
    %
    For a more mathematical and complete presentation, I can recommend the classic mathematical textbook by Hardy \cite{Hardy_1991} and the classic physics articles of \Reffs{Dunne:2012ae,Dorigoni:2014hea};
    %
    a full list of the many wonderful resources for resummation beyond these, is far beyond our scope.
}

@@

\begin{figure}[t!]
    \centering
    \includegraphics[width=0.7\textwidth]{example-image-a}
    \caption[
        Regions of the \(1/z\)-\(s\) plane associated with our approximations.
        %
        Adapted from \Reff{Collins:1984xc} \sam{incomplete}
    ]
    {
        Regions of the \(1/x\)-\(s\) plane associated with the approximations use in this thesis.
        %
        Adapted from \underline{QCD and Collider Physics} \cite{Collins:1984xc}.  \sam{complete -- see page 132, fig 4.18}
    }
    \label{fig:dlla-plane}
\end{figure}

@@

In this section, we discuss why and how we may sew together splitting functions in order to characterize the partonic cascade.
%
Recall from \Sec{splitting-functions} that splitting functions were defined in terms of amplitudes for the production of \textit{on-shell} final states, \(\mathcal{M}_{\ell^* \to i j}\).
%
In \Prop{splitting-probability-main}, we then wrote the full differential cross section for a process producing \(N\) particles, two of which were a collinear pair \((i_1, j_1)\), in a factorized form:
%
\begin{align}
    \dd \sigma_N
    =
    \dd \sigma_{N-1}
    \,
    \dsigmatilde_{i_1\,i_2}
    \,,
\end{align}
where \(\sigma_{N-1}\) is the ``differential cross section'' when the pair \((i_1,j_1)\) have been replaced by the off-shell \(\ell^*\), and is associated with the production of \(N-1\) particles, and \(\dsigmatilde_{i_1\, i_2}\) is the splitting distribution (as in \Prop{splitting-probability-main} of \Sec{splitting-functions}) associated with the splitting.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\textwidth]{example-image-a}
    \caption[The ripple picture of the partonic cascade \sam{incomplete}]{\sam{The ripple picture of the partonic cascade}}
    \label{fig:}
\end{figure}

@@

MLL calculations of additive jet substructure observables capture nearly all of the effects of a \glslink{accuracy}{next-to-leading logarithmic (NLL)} calculation \cite{Marzani:2019hun}.
%
Missing, however, are \vocab{non-global logarithms} -- contributions to jet substructure from partonic radiation in which a branch of the partonic tree of emissions occurs at a wider angle than would be captured by the jet, but one of whose children re-enters the jet cone.\cite{Dasgupta:2001sh,Appleby:2002ke,Weigert:2003mm,Rubin:2010fc,Banfi:2010pa,Hornig:2011iu,Kelley:2011aa,Hatta:2013iba,Schwartz:2014wha,Khelifa-Kerfa:2015mma,Larkoski:2016zzc,Marzani:2019hun,Banfi:2021owj,Banfi:2021xzn}

@@

\remark{}{
    To include running coupling effects and work towards an MLL description of additive jet observables, we notice that the splittings of perturbative QCD should be governed by an \textit{effective coupling} \(\alpha_s(\kappa)\), where \(\kappa = \kappa(z,\theta)\) is a scale associated with the splitting.
    %
    The result would involve integrals containing terms of the form \(\int \dd z \, \dd \theta \, \alpha_s(\kappa) \, p(z) / \theta\).
    %
    The precise value we should choose for \(\kappa\) in order to account for higher-order effects is not obvious, but \Reff{Amati:1980ch} showed that \(\kappa\) should be given by the transverse momentum of the splitting in order to minimize the effects of large logarithms in perturbative calculations:
    \begin{align}
        \kappa \approx Q z(1-z)\sin\theta \approx Q z \theta
        \,.
    \end{align}
    %
    In particular, QCD correlations and cross sections that use \(\alpha_s\) evaluated at a scale \(\kappa\) generically include logarithms of the form \(\log(p_{\perp} / \kappa)\).
    %
    To make these logarithms small, one may choose \(\kappa \sim p_\perp\), which then requires that we evaluate the strong coupling at the scale \(p_\perp\) as well.
    %
    This prescription provides a straightforward procedure for understanding higher-order effects with \glspl{substructure-diagram}, and can be extended to higher perturbative accuracy with the Catani-Marchesini-Webber (CMW) prescription \cite{Catani:1990rr}, which achieves two-loop accuracy for the running of \(\alpha_s\), and to qualitatively include non-perturbative effects by \textit{freezing} the coupling, as discussed in \App{soft-distortions}.
    %
    As a reminder, the one-loop running of \(\alpha_s\) is captured by
    \begin{align}
        \alpha^{\rm 1-loop}_s(\kappa)
        =
        \frac{\alpha_s(Q)}{1 + \alpha_s(Q) \beta_0 \log(\frac{\kappa}{Q})/2\pi}
        ,
    \end{align}
    where \(\beta_0 = \frac{11}{3}C_A - \frac{4}{3} T_f n_f\) is a coefficient appearing in the QCD beta function: \(\beta(\alpha_s) = -\beta_0 \alpha_s^2/2\pi + \mathcal{O}(\alpha_s^3)\).
}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.8\textwidth]{example-image-a}
    \caption[A visualization of the simplifications enabled by additive observables. sam{incomplete}]
    {\sam{simplifications of additive observables in partonic-cascade computations}}
    \label{fig:cascade-simplifications}
\end{figure}

@@

The \gls{parton-to-parton} is most easily characterized in terms of its \vocab{Mellin moments}, which directly capture the scaling behavior of a function (i.e. the behavior of a function as one zooms in).%
\footnote{
    Concretely, homogenous monomials, such as \(x^\ell\), have extremely simple scaling behavior:
    %
    as one scales \(x\) by a factor of \(a\), one obtains a deceptively simple relation \((a x)^\ell = a^\ell x^\ell\);
    %
    if \(a < 1\), we have ``zoomed in'' to the behavior of the function near \(x = 0\).
    %
    We say that these simple monomials are \textit{eigenfunctions of the scaling} (or dilatation) \textit{operator}.
    %
    The scaling behavior of a more complicated function \(f(x)\) -- e.g. a concrete relationship between \(f(ax)\) and \(f(x)\) -- can then be captured explicitly if it is known how \(f(x)\) can be composed in terms of the simple building blocks \(x^\ell\).
    %
    Luckily, \textit{the Mellin moments of a function \(f(x)\) precisely captures how \(f(x)\) is composed of the simple building blocks \(x^\ell\), and therefore provides a complete and simple characterization of its scaling behavior.}
    %
    See \App{mellin} for a brief review.
}
%
Mellin moments are wonderful tools for capturing fractal structures in a wide variety of applications, and for the mathematically prodigious, it may be no surprise that they appear here.

@@

\begin{proposition}{Parton-to-Parton Fragentation at LL}{}
\begin{align}
    \label{eq:mellin_transform_defn}
    \hat{F}_{j \leftarrow i}(m;\,\rsub \leftarrow \Rjet)
    &:=
    \int_0^1 \dd x_j \, x_j^{m-1}
    \,
    F_{j \leftarrow i}(x_j;\,\rsub \leftarrow \Rjet)
    \\
    \label{eq:ll_fragmentation_function}
    &=
    \le(\frac{\alpha_s\le(Q\,\rsub\ri)}{\alpha_s\le(Q\,\Rjet\ri)}\ri)
    ^
    {\frac{2 \hat{p}(m)}{\beta_0}}
    _{j\leftarrow i}
    \,,
\end{align}
where \(Q\) is the energy carried by the initiating parton \(i\) and the subscript \(j \leftarrow i\) indicates the indices of a matrix exponential in the final line.
\end{proposition}

@@

\begin{proof}
Recalling that the jet is formed by partonic splittings which become (at LL) successively narrower, we write:
\begin{align}
    F_{f \leftarrow i}(x_f; \rsub \leftarrow \Rjet)
    &=
    \delta(1-x_f) \, \delta_{fi}
    \,\,\,
    +
    \,\,\,
    \sum_{n = 1}^\infty
    \le( 4 a_s \ri)^n
    \int^{\Rjet}_{\rsub} \frac{\dd\theta_1}{\theta_1}
    \,\,
    \int^{\theta_1}_{\rsub} \frac{\dd\theta_2}{\theta_2}
    \,\,\,
    \cdots
    \,\,
    \int^{\theta_{n-1}}_{\rsub}
    \,\,
    \frac{\dd\theta_n}{\theta_n}
    \notag
    \\
    &\qquad\qquad\qquad\qquad\qquad
    \label{eq:shower_fragmentation}
    \times
    \int_0^1 \dd x_1
    \,
    \le(\sum_{k_1}\,P_{j_1 k_1 \leftarrow i}(x_1)\ri)
    \\
    \notag
    &\qquad\qquad\qquad\qquad\qquad\qquad
    \times
    \,\,
    \cdots
    \,\,
    \int_0^1 \dd x_n
    \le(\sum_{k_n}\,P_{f\,k_n \leftarrow j_{n-1}}(x_n)\ri)
    \\
    \notag
    &\qquad\qquad\qquad\qquad\qquad
    \times
    \delta\le(x_f - \prod_{j=1}^n x_j\ri)
     ,
\end{align}
visualized diagrammatically in \Fig{shower:cartoon:fragmentation}.
%
The first term on the right-hand-side of \Eq{shower_fragmentation} represents the possibility of no splitting, where parton \(f\) is \emph{equal} to parton \(i\).
%
The terms within the sum on \(n\) each represent the possibility of \(n\) splittings in the parton shower along the path traced from parton \(i\) to parton \(f\).
%
For each term in the sum over \(n\), each of the \(n\) splittings has a probability density in its angle and energy fraction determined by \Prop{splitting-probability-main}, and the angular ordering \(\theta_1 > \theta_2 > \cdots > \theta_n\) is enforced by the bounds of integration on each of the angular integrals.
%
The delta function, \(\delta\le(x_f - \prod_{j = 1}^n x_j\ri)\) indicates that the final energy fraction of parton \(f\) is equal to the product of the energy fractions along the path from \(i\) to \(f\).

@@

To evaluate \Eq{shower_fragmentation}, we perform the angular integrals over the \(\{\theta_k\}_{k = 1}^n\) and use the definition of the inclusive splitting functions in \Eq{inclusive_splitting_defn}.
%
We then take Mellin moments of \(F_{f\leftarrow i}(x_f)\) in order to integrate over the delta function \(\delta \le(x_f - \prod_{k=1}^n x_k\ri)\) and enforce the relation \(x_f^{m-1} = \prod_{k=1}^n x_k^{m-1}\).
%
After the dust settles, we obtain the following expression for the Mellin moments of the parton-to-parton fragmentation function:
\begin{subequations}
\label{eq:ll_fragmentation_repeat}
\begin{align}
    \label{eq:ll_fragmentation_angle}
    \hat{F}_{f \leftarrow i}(m;\,\rsub \leftarrow \Rjet)
    &=
    \sum_{n=0}^\infty
    \le(-4\as\ri)^n
    \frac{\log^n\le(\rsub/R\ri)}{n!}
    \le(
        \int_0^1 \dd z\,
        z^{m-1} p(z)
    \ri)^n_{f\leftarrow i}
    \\
    &\approx
    \exp\le[
        \frac{2\hat{p}(m)}{\beta_0}
        \log\le(
        \frac{
            \alpha_s\le(Q\,\rsub\ri)
        }{
            \alpha_s\le(Q\,\Rjet\ri)
        }\ri)
    \ri]_{f \leftarrow i}
    ,
\end{align}
\end{subequations}
where we have used the one-loop expression for \(\alpha_s(\mu)\) in \Eq{alphas_1loop} to make the replacement \(
    \log\big(
        \alpha_s\le(Q\,\rsub\ri)
        \,/\,
        \alpha_s\le(Q\,\Rjet\ri)
    \big)
    =
    -2 \beta_0 \, \as \,
    \log\le(\rsub/R\ri)
    \,
    +
    \,
    \mathcal{O}(\alpha_s^2)
\), recovering the result claimed in \Eq{ll_fragmentation_function}, up to higher order corrections in \(\alpha_s\) that we neglect at this accuracy.
\end{proof}

%\begin{exercise}
%    % https://www.hep.phy.cam.ac.uk/theory/webber/QCDlect3.pdf#page=19
%    Argue that the physics of very soft splittings -- the \(z \to 0\) limit -- is captured by the limit \(m \to 1\).
%    %
%    Based on physical expectations, do you expect the \(m=1\) moments of any \gls{qcd} splitting functions to diverge?
%    %
%    Check your intuition against the results of \Tab{inclusive-splitting}.
%\end{exercise}

Applying the principles of renormalization to \Eqs{ll_fragmentation_function}{ll_fragmentation_repeat}, we can ask how the process of partonic fragmentation changes as we change the angular resolution of our ``measurements'' (i.e. the jet radius \Rjet{} and the subjet radius \rsub{}).
%
In particular, we can use \Eq{ll_fragmentation_angle} to ask how the fragmentation process changes as a function of \(\Rjet\) or \(\rsub\):
\begin{subequations}
\begin{align}
    \label{eq:fragmentation_dglap_upper}
    \frac{\dd}{\dd\log\le(Q\,\Rjet\ri)} \hat{F}(m;\,\rsub\leftarrow \Rjet)
    &=
    \frac{\alpha_s(Q\,\Rjet)}{\pi}
    \,\,
    \hat{p}(m)
    \,
    \hat{F}(m;\,\rsub\leftarrow \Rjet)
    \\
    \label{eq:fragmentation_dglap_lower}
    \frac{\dd}{\dd\log\le(Q\,\rsub\ri)} \hat{F}(m;\,\rsub\leftarrow \Rjet)
    &=
    -\frac{\alpha_s(Q\,\rsub)}{\pi}
    \,\,
    \hat{p}(m)
    \,
    \hat{F}(m;\,\rsub\leftarrow \Rjet)
    ,
\end{align}
\end{subequations}
where we have suppressed the indices of \(\hat{p}\) and \(\hat{F}\) for brevity.
%
Amazingly, we have recovered the celebrated \glslink{dglapeqn}{Dokshitzer-Gribov-Lipatov-Altarelli-Parisi (DGLAP) equations} \cite{Gribov:1972ri,Dokshitzer:1977sg,Altarelli:1977zs} for our parton-to-parton fragmentation functions:
\begin{align}
    \frac{\dd}{\dd\log\le(Q \Rjet\ri)}
    F_{f\leftarrow i}(z; \rsub \leftarrow \Rjet)
    =
    \frac{\alpha_s(Q\Rjet)}{\pi}
    \int_0^1
    \dd \frac{\dd y}{y}
    p_{j k}(y)
    F_{j\leftarrow i}\le(\frac{z}{y}; \rsub \leftarrow \Rjet\ri)
    \\
    \frac{\dd}{\dd\log\le(Q \rsub\ri)}
    F(z, \rsub \leftarrow \Rjet)
    =
    -
    \frac{\alpha_s(Q\rsub)}{\pi}
    \int_0^1
    \dd \frac{\dd y}{y}
    p_{j k}(y)
    F_{j\leftarrow i}\le(\frac{z}{y}; \rsub \leftarrow \Rjet\ri)
    \,,
\end{align}
where we have left a sum on \(k\) implicit.
%
More generally, \glspl{dglapeqn} state that the distribution of energy fractions \(z\) of partons inside a high energy composite object \(A\) obey similar integro-differential equations in which \(Q\Rjet\) is replaced by a high energy scale \(E_A\) associated with the energy of the composite object.

@@

\begin{figure}[]
    \centering
    \subfloat[]{
        % Subfigure graphic
        \includegraphics[width=.48\textwidth]{example-image-a}
        \label{fig:reclustering}
    }
    \subfloat[]{
        % Subfigure graphic
        \includegraphics[width=.48\textwidth]{example-image-a}
        \label{fig:declustering}
    }
    \caption[Cartoons depicting re-clustering and de-clustering. \sam{incomplete}]{
        \sam{Cartoon depicting reclustering and declustering}
    }
    \label{fig:re-and-de-clustering}
\end{figure}

@@

    Any algorithm which leverages \gls{declustering} is called a \vocab{de-clustering algorithm}.
    %
    The \gls{declustering} procedure is visualized in \Fig{declustering}.
\end{definitionbox}

@@

% \begin{figure}[]
%     \centering
%     \includegraphics[width=0.8\textwidth]{example-image-a}
%     \caption{{Re-weighting}}
%     \label{fig:reweighting}
% \end{figure}
